Douglas-complex fire smoke and cardiopulmonary morbidity

### 2018-05-16 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
updated
saved some plots as png.

smoke_map
```

@@

```{r geofacet time series of pm}
# use or_counties_grid from geo_facet 
or_grid <- geofacet::or_counties_grid1 %>% 
  mutate(name = ifelse(name == "HoodRiver", "Hood River", name))

>>>>

smoke_map
# save figure
ggsave(filename = "./smoke_map.png", plot = smoke_map)
```

@@

```{r geofacet time series of pm}
# use or_counties_grid from geo_facet 
or_grid <- geofacet::us_or_counties_grid1 %>% 
  mutate(name = ifelse(name == "HoodRiver", "Hood River", name))
